### 2017-05-08 experiments.tex
ok to ship

Our primary experiments are based on subjects used in the only previous study of compiler fuzzer taming \cite{PLDI13}.  Of the three data sets examined in that paper, this paper considers two:  faults and tests cases for SpiderMonkey 1.6, Mozilla's JavaScript engine, with tests generated by {\tt jsfunfuzz} \cite{jsfunfuzz}, and \emph{wrong code} faults and test cases for GCC 4.3.0, with tests generated by Csmith \cite{csmith}.  GCC 4.3.0 crash faults were essentially perfectly localized by previous approaches.  Faults that produce a crash are also likely to be easier to debug than purely semantic problems, such as many of the SpiderMonkey faults and all GCC wrong code faults.

We applied our metric to two of the datasets used in the previous study of compiler fuzzer taming \cite{PLDI13}: faults and tests cases for SpiderMonkey 1.6, Mozilla's JavaScript engine, with tests generated by {\tt jsfunfuzz} \cite{jsfunfuzz}, and \emph{wrong code} faults and test cases for GCC 4.3.0, with tests generated by Csmith \cite{csmith}.   We did not use the crash faults from that data set, as these are in practice fairly easy to identify by hand (and perfectly identified by previous metrics), and also typically easy to debug.

@@

The APFD (Average Percent Faults Detected) values shown in the graphs are based on the measure  introduced by Rothermel et al. to evaluate test case prioritization methods \cite{APFD}.  This is a somewhat better summary of results than the raw curve areas used in previous work \cite{PLDI13}.  APFD, as the name suggests, shows the percent of all faults discovered at the ``average'' point on the curve, by comparing the curve's area to an ideal curve, with interpolation.  A simpler (but less informative) way to compare the curves is to note that the mutation-based metric's curve is above the best previous curve at 60\% of data points.
%\footnote{The details of APFD calculation are slightly involved, and the interpolation and perfect curve are not exact fits for fuzzer taming; nonetheless the basic method summarizes curves fairly well and is standard in the testing literature for similar problems \cite{issta14}.}.

@@

There were 377,679 GCC mutants, based on 424,186 lines of code in C and header files. Of these mutants, 73,016 were covered by some failing test case.  Of these mutants, 41,385 survived a GCC bootstrap build, compiled hello world, and passed a GCC test suite.  Of these mutants, 3,232 (7.8\%) repaired at least one test case.  Figure \ref{gcccurves} shows discovery curves for the mutant repair metric vs. the best PLDI 2013 curve, Euclidean distance over function coverage vectors \cite{PLDI13}.  GCC's APFD improvement is larger than that for SpiderMonkey, but its early curve is worse compared to the PLDI 2013 curve.  Over all, again the curve is better than the best PLDI 13 curve at 60\% of all points.  Using the hypothetical model where a user stops examining tests after a plateau of size 10, the user of the mutant-based taming will see 18 distinct faults by examining 25 tests, and the user of the function coverage based taming will see 20 faults after examining 45 tests.  If a user gives up after a plateau of size 5, our approach again lets a user examine 18 faults over 25 tests.  Function coverage only yields 16 faults over 31 tests.

@@

In one sense, the discovery curve improvements here are practically very useful, but not extremely large in a relative sense.  The SpiderMonkey curve has an APFD only slightly more than 2\% better than the best result from previous FPF efforts.  For GCC, APFD improves by 6.4\%.  However, the comparison is with the very \emph{best} curve chosen after running more than 16 different metrics.  In practice, users simply do not know ground truth to rank curves, thus Chen et al. \cite{PLDI13} do not really give a practical approach to distance metric selection in their PLDI work.  The best methods for different subjects varied widely, even in such difficult-to-understand ways as less-fine-grained coverage providing better results in some cases, but worse in other cases.   In practice, their work established that FPF could produce good curves, but gave very little useful guidance for choosing a metric for actual use of the technique, since trying multiple metrics is impractical, since a user has to examine each curve.  \comment{It also included methods such as comparing output signatures that are inapplicable to differential testing in most cases, the most critical compiler application.}  This paper presents a single curve using a universal metric, and achieves a 2-6\% percentage point improvement over the best of more than 16 different metrics studied in the previous work; our improvements over any single ``reasonable'' method applied to both problems would be considerably larger (for instance, using the most obvious basis, line coverage, we see more than 17\% improvement).  Moreover, the improvement is, for our subject programs, reliable:  choosing random subsets of the full data set, the difference in mean APFD from best-previous method is around 3\%, and statistically significant.

@@

@@

The other way to think about {\bf Repair} for the non-compiler faults especially, is as a very \emph{cautious} localization.  It only uses mutants that repair a failure, and, because it is clear that, in general, failing tests contain far more information about faults than passing tests, it only uses information from failures (other than using passing tests to prune mutants that kill some passing tests, again a principle of discarding potentially confusing information).  This results in {\bf Repair} either providing a ``useful'' localization or almost no localization information at all to mislead a user, for the non-compiler faults, which user studies and surveys suggest is the ideal behavior due to the cost of false positives in localization \cite{AutoHelp,Kochhar}.  This is basically a trade-off.  MUSE, MUSEUM, and Metallaxis-FL provide localization for many more faults, in a more diverse range of settings (with single failing tests, no repairs, etc.), and using more diverse information --- but, in cases where {\bf Repair} provides a localization, it seems to often be higher quality due to its restriction to high-signal source of information (mutants repairing failing tests, only).  In settings, unlike compilers, where there are relatively few repairs, {\bf Repair} also produces very little incorrect information, and so has a low cost to the user in terms of wasted attention.  Note that our heuristic to stop reading after 5 wrong localizations is not even needed for all but one CoreUTILS fault --- {\bf Repair} suggests 1-3 statements at most.

@@

{ For the compiler faults, if any repair for a failure modified a faulty statement, {\bf Repair} always ranked it in the top 34 localizations, ranked it in the top 5 in 6 of 10 such cases, and 3 times ranked it 1st.  MUSEUM, in contrast, ranked one such repair 195th, never ranked a fault in its top 3 statements, and only ranked a fault in its top 5 statements twice.  Of course, MUSEUM might be suffering from a lack of mutation operators, but in some cases this is unlikely due to the nature of the repairs.

@@

The largest threat to validity is that this paper's conclusions rely on only two data sets for compilers.  The fault ground truths are possibly imperfect, due to the complex change history, and it was not possible to produce good patches for all faults, limiting our analysis of compiler fault localization.    The comparison with other fault localization methods is also limited:  our compiler experiments limit the mutation budget in ways that may weaken MUSE and MUSEUM effectiveness, and the results using fault and mutant data sets from other studies provide few faults, no multi-fault problems, and very few multi-failure problems, limiting {\bf Repair} effectiveness.   It is also possible that faults in the framework used for experiments introduced errors into the data.  In order to check for these problems, we will make the raw data for a re-analysis available on request.

>>>>

Our primary experiments are based on subjects used in the only previous study of compiler fuzzer taming \cite{PLDI13}.  Of the three data sets examined in that paper, this paper considers two:  faults and tests cases for SpiderMonkey 1.6, Mozilla's JavaScript engine, with tests generated by {\tt jsfunfuzz} \cite{jsfunfuzz}, and \emph{wrong code} faults and test cases for GCC 4.3.0, with tests generated by Csmith \cite{csmith}.  GCC 4.3.0 crash faults were essentially perfectly localized by previous approaches.  In fact, on examination, only two of the 11 crash bugs are not distinguished by simply examining the crash message.  Faults that produce a crash are also likely to be much easier to debug than semantic problems such as all of the GCC wrong code bugs and most of the JavaScript faults --- e.g., following a dynamic slice might well suffice.

\comment{
We applied our metric to two of the datasets used in the previous study of compiler fuzzer taming \cite{PLDI13}: faults and tests cases for SpiderMonkey 1.6, Mozilla's JavaScript engine, with tests generated by {\tt jsfunfuzz} \cite{jsfunfuzz}, and \emph{wrong code} faults and test cases for GCC 4.3.0, with tests generated by Csmith \cite{csmith}.   We did not use the crash faults from that data set, as these are in practice fairly easy to identify by hand (and perfectly identified by previous metrics), and also typically easy to debug.  }

@@

The APFD (Average Percent Faults Detected) values in the graphs are based on the measure  introduced by Rothermel et al. for evaluating test case prioritization methods \cite{APFD}.  APFD is a somewhat better summary of results than the raw curve areas used for evaluation in previous work \cite{PLDI13}.  APFD, as the name suggests, measures the percent of all faults discovered at the ``average'' point on the curve, by comparing the curve's area to an ideal curve, with interpolation.  A simpler (but less informative) way to compare the curves is to note that the mutation-based metric's curve is above the best previous curve at 60\% of data points.
%\footnote{The details of APFD calculation are slightly involved, and the interpolation and perfect curve are not exact fits for fuzzer taming; nonetheless the basic method summarizes curves fairly well and is standard in the testing literature for similar problems \cite{issta14}.}.

@@

There were 377,679 GCC mutants, based on 424,186 lines of code in C and header files. Of these mutants, 73,016 were covered by some failing test case.  Of these mutants, 41,385 survived a GCC bootstrap build, compiled hello world, and passed a GCC test suite.  Of these mutants, 3,232 (7.8\%) repaired at least one test case.  Figure \ref{gcccurves} shows discovery curves for the mutant repair metric vs. the best PLDI 2013 curve, Euclidean distance over function coverage vectors \cite{PLDI13}.  GCC's APFD improvement is larger than that for SpiderMonkey, but its early curve (first 15 tests) is worse compared to the PLDI 2013 curve, but still has a maximum gap of only 2 redundant tests vs. 4 for PLDI 13.  Over all, again the curve is better than the best PLDI 13 curve at 60\% of all points.  Using the hypothetical model where a user stops examining tests after a plateau of size 10, the user of the mutant-based taming will see 18 distinct faults by examining 25 tests, and the user of the function coverage based taming will see 20 faults after examining 45 tests.  If a user gives up after a plateau of size 5, our approach again lets a user examine 18 faults over 25 tests.  Function coverage only yields 16 faults over 31 tests.

@@

In one sense, the discovery curve improvements here are practically very useful, but not extremely large in a relative sense.  The SpiderMonkey curve has an APFD only slightly more than 2\% better than the best result from previous FPF efforts.  For GCC, APFD improves by 6.4\%.  However, the comparison is with the very \emph{best} curve chosen after running more than 16 different metrics.  In practice, users simply do not know ground truth to rank curves, thus Chen et al. \cite{PLDI13} do not really give a practical approach to distance metric selection in their PLDI work.  The best methods for different subjects varied widely, even in such difficult-to-understand ways as less-fine-grained coverage providing better results in some cases, but worse in other cases.   In practice, their work established that FPF could produce good curves, but gave very little useful guidance for choosing a metric for actual use of the technique, since trying multiple metrics is impractical: a user has to examine each curve.  \comment{It also included methods such as comparing output signatures that are inapplicable to differential testing in most cases, the most critical compiler application.}  This paper presents a single curve using a universal metric, and achieves a 2-6\% percentage point improvement over the best of more than 16 different metrics studied in the previous work; our improvements over any single ``reasonable'' method applied to both problems would be considerably larger (for instance, using the most obvious basis, line coverage, we see more than 17\% improvement).  Moreover, the improvement is, for our subject programs, reliable:  choosing random subsets of the full data set, the difference in mean APFD from best-previous method is around 3\%, and statistically significant.

@@

For the compiler faults, if any repair for a failure modified a faulty statement, {\bf Repair} always ranked it in the top 34 localizations, ranked it in the top 5 in 6 of 10 such cases, and 3 times ranked it 1st.  MUSEUM, in contrast, ranked one such repair 195th, never ranked a fault in its top 3 statements, and only ranked a fault in its top 5 statements twice.  Of course, MUSEUM might be suffering from a lack of mutation operators, but in some cases this is unlikely due to the nature of the repairs.  For the CoREBench faults, {\bf Repair} produced more than twice as many perfect localizations as the other methods, though it also did not provide any ranking for a fault in a large number of cases.

@@

The other way to think about {\bf Repair} for the non-compiler faults especially, is as a very \emph{cautious} localization.  It only uses mutants that repair a failure, and, because it is clear that, in general, failing tests contain far more information about faults than passing tests, it only uses information from failures (other than using passing tests to prune mutants that kill some passing tests, again a principle of discarding potentially confusing information).  This results in {\bf Repair} either providing a ``useful'' localization or almost no localization information at all to mislead a user, for the non-compiler faults, which user studies and surveys suggest is the ideal behavior due to the cost of false positives in localization \cite{AutoHelp,Kochhar}.  This is basically a trade-off.  MUSE, MUSEUM, and Metallaxis-FL provide localization for many more faults, in a more diverse range of settings (with single failing tests, no repairs, etc.), and using more diverse information --- but, in cases where {\bf Repair} provides a localization, it seems to often be higher quality due to its restriction to a high-signal source of information (mutants repairing failing tests, only).  In settings, unlike compilers, where there are relatively few repairs, {\bf Repair} also produces very little incorrect information, and so has a low cost to the user in terms of wasted attention.  Note that our heuristic to stop reading after 5 wrong localizations is not even needed for all but one CoREBench fault --- {\bf Repair} suggests 1-3 statements at most.

@@

\comment{ For the compiler faults, if any repair for a failure modified a faulty statement, {\bf Repair} always ranked it in the top 34 localizations, ranked it in the top 5 in 6 of 10 such cases, and 3 times ranked it 1st.  MUSEUM, in contrast, ranked one such repair 195th, never ranked a fault in its top 3 statements, and only ranked a fault in its top 5 statements twice.  Of course, MUSEUM might be suffering from a lack of mutation operators, but in some cases this is unlikely due to the nature of the repairs.  }

@@

The largest threat to validity is that this paper's conclusions rely on only two data sets for compilers, and a small number of non-compiler faults.  The compiler ground truths are possibly imperfect, due to the complex change history, and it was not possible to produce good patches for all faults, limiting our analysis of compiler fault localization.    The comparison with other fault localization methods is also limited:  our compiler experiments limit the mutation budget in ways that may weaken MUSE and MUSEUM effectiveness, and the results using fault and mutant data sets from other studies provide few faults, no multi-fault problems, and very few multi-failure problems, limiting {\bf Repair} effectiveness.   It is also possible that faults in the framework used for experiments introduced errors into the data.  In order to check for these problems, we will make the raw data for a re-analysis available on request.

### 2017-05-08 introduction.tex
ok to ship

Automated test generators tend to produce many failures, which correspond to far fewer faults.  The distribution of faults in a set of failures tends to follow a strong power-law curve, where a few faults account for most failures, and many or even most faults have only 1 or 2 associated failures (even in a set of 1,000 or more test cases) \cite{PLDI13}.  Looking at all the failures to find  distinct faults is impractical.  It is also impractical to apply the iterative approach:  first, fix one test's fault; then re-run all tests, until all tests pass.  There may be some (possibly known) faults that are very difficult to fix. As of 1/16/2017, clang had 109 unresolved, assigned bugs, some dating to 2008 \cite{clangbugs}.  Knowing if a randomly generated test case is an instance of a known failure can be difficult, and fixing long-standing problems to improve bug triage is unlikely.    A research group with a novel fault-detection technique \cite{csmith,ISSTA12,ZhendongPLDI} may dump dozens of new faults on a project at once, and high priority faults may be hidden by stubborn low-priority faults.

@@

The key insight of this paper is based on an idea with numerous possible applications: \emph{if two test cases that fail can be made to succeed by the same small modification to the original program $P$, this provides evidence that they fail due to the same fault}.  The idea is hardly controversial:  most developers determine if they have fixed all faults in a set of failing test cases by re-running the tests after they fix at least one fault.  As a method for fuzzer taming or debugging assistance, however, this is useless.  Fortunately, developer-provided patches are not the only source of changes to a program.  Mutation analysis \cite{demillo1978hints,budd1980theoretical} applies large numbers of small syntactic changes to a program, usually to evaluate a test suite \cite{mutant,justmutants}.  Some recent work has also considered these changes as a source of fixes or localizations for program faults \cite{achour,multilingual,MUSE,DebroyMutant}.  Our experience, as well as empirical data \cite{GopinathMutants}, suggests that very few compiler faults are due to the kind of simple syntactic changes found in mutants.  However, what should matter is that failures, which correspond to faults, can be made to succeed.  When a test case $t$ fails for program $P$ but succeeds for mutant $m$ of $P$ we say that $m$ \emph{repairs} $t$.  In most cases this does not mean that $m$ is the inverse of a fault, but that $m$ somehow avoids the consequence of a fault.  It is not important that repairs actually fix anything, if all we seek is a way to decide whether failures are due to the same fault.

@@

This leads to the idea of comparing executions by their response to mutants.   In the presence of multiple correctness properties, in principle any two executions can be compared, not just two failures, since a mutant can cause a failure to violate additional or different properties.   However, for practical purposes the most interesting implication is that if two failing test cases can be made to differ as to whether they fail by a modification of $P$, this provides evidence that they fail due to different faults.

@@

This paper investigates the utility of using distance metrics based on the causal approach suggested above.  We show that such a metric can improve, in a statistically significant way, the ability to distinguish tests based on which faults they trigger.  Furthermore, fault localization based on the same metrics can successfully pinpoint the location of some compiler faults sufficiently to be likely to substantially aid debugging, and, when applicable, performs very well for some faults studied in recent papers on mutant-based fault localization.

@@

The contributions of this paper include our ideas about how to measure distance between program executions, but more importantly some practical proposals for using such a metric in compiler fuzzer taming and fault localization.  Our experimental results show that, for two realistic complex compilers, Mozilla's SpiderMonkey 1.6 JIT for JavaScript and GCC 4.3.0, using mutant response metrics improves FPF-based fuzzer taming over best previous results \cite{PLDI13}, in multiple ways.  Our best preliminary localization approach also compares favorably to state-of-the-art fault localization techniques \cite{MUSE,multilingual,Metallaxis}, albeit with a more limited applicability (but a lower cost).

>>>>

Automated test generators tend to produce many failures, which correspond to far fewer faults.  The distribution of faults in a set of failures tends to follow a strong power-law curve, where a few faults account for most failures, and many or even most faults have only 1 or 2 associated failures (even in a set of 1,000 or more test cases) \cite{PLDI13,OneTest}.  Looking at all the failures to find  distinct faults is impractical.  It is also impractical to apply the iterative approach:  first, fix one test's fault; then re-run all tests, until all tests pass.  There may be some (possibly known) faults that are very difficult to fix. As of 5/8/2017, clang had 107 unresolved, assigned bugs, some dating to 2008 \cite{clangbugs}.  Knowing if a randomly generated test case is an instance of a known failure can be difficult, and fixing long-standing problems is unlikely.    Applying a novel fuzzing technique \cite{csmith,ISSTA12,ZhendongPLDI} may dump dozens of new faults on a project at once, and high priority faults may be hidden by stubborn low-priority faults.

@@

The methods we propose are based on an idea with numerous possible applications: \emph{if two test cases that fail can be made to succeed by the same small modification to the original program $P$, this provides evidence that they fail due to the same fault}.  The idea is hardly controversial:  most developers determine if they have fixed all faults in a set of failing test cases by re-running the tests after they fix at least one fault.  As a method for fuzzer taming or debugging assistance, however, this is useless.  Fortunately, developer-provided patches are not the only source of changes to a program.  Mutation analysis \cite{demillo1978hints,budd1980theoretical} applies large numbers of small syntactic changes to a program, usually to evaluate a test suite \cite{mutant,justmutants}.  Some recent work has also considered these changes as a source of fixes or localizations for program faults \cite{achour,multilingual,MUSE,DebroyMutant}.  Our experience, as well as empirical data \cite{GopinathMutants}, suggests that very few compiler faults are due to the kind of simple syntactic changes found in mutants.  However, what should matter is that failures, which correspond to faults, can be made to succeed.  When a test case $t$ fails for program $P$ but succeeds for mutant $m$ of $P$ we say that $m$ \emph{repairs} $t$ (in practice, we will usually restrict this to unkilled mutants $m$).  In most cases this does not mean that $m$ is the inverse of a fault, but that $m$ somehow avoids the consequence of a fault.  It is not important that repairs actually fix anything, if all we seek is a way to decide whether failures are due to the same fault.

@@

This leads to the general idea of comparing any two executions by their response to mutants, since a mutant can cause a passing or failing test to violate more/different properties.   However, for practical purposes the most interesting implication is that if two failing test cases can be made to differ as to whether they fail by a mutant, this provides evidence that they fail due to different faults.

@@

This paper investigates the utility of using distance metrics based on the causal approach suggested above.  We show that such a metric can improve, in a statistically significant way, the ability to distinguish tests based on which faults they trigger.  Furthermore, fault localization based on the same metrics can successfully pinpoint the location of some compiler faults sufficiently to be likely to substantially aid debugging, and, when applicable, performs very well for some faults studied in recent papers on mutant-based fault localization \cite{multilingual,Papadakis}.

@@

The contributions of this paper include our ideas about how to measure distance between program executions, but more importantly some practical proposals for using such a metric in compiler fuzzer taming and fault localization.  Our experimental results show that, for two realistic complex compilers, Mozilla's SpiderMonkey 1.6 JIT for JavaScript and GCC 4.3.0, using mutant response metrics improves FPF-based fuzzer taming over best previous results \cite{PLDI13}, in multiple ways.  Our fault localization approach also compares favorably to state-of-the-art fault localization techniques \cite{MUSE,multilingual,Metallaxis}, albeit with a more limited applicability (but also a lower cost).

### 2017-05-08 localizations.tex
ok to ship

Parnin and Orso note that most popular methods are
statistical and tend to simply provide an ordered list of statements
to examine.  These statements are not guaranteed to be essentially
related to the fault --- with many techniques, the statements are,
too often, code that executes as a consequence of the fault, code
accidentally executed with the fault, and so forth.  Second, most
evaluations of fault localization have been performed over programs
where it is not clear that debugging is extremely hard, vs. the time
spent applying automated localization and establishing effective
(automated) testing to support automated localization.  Compiler
debugging, on the other hand, especially for subtle optimization-based
problems that produce incorrect code (vs. simple crashes) is generally
known to be difficult.
Researchers reporting subtle compiler bugs often observe the time from
reporting a fault to its correction, even once the fault is assigned,
to be lengthy, and the resulting patches are sometimes thousands of
lines \cite{PLDI13}.  Important compilers, whether JITs where security is paramount
or C compilers used to compile core systems code, also tend to already
be the
subjects of extensive automated testing \cite{jsfunfuzz,csmith}.

@@

In general, we expect {\bf Repair} to be used in the context of
compiler (or other complex system) fuzzing, where there are numerous
failing tests, likely from multiple faults.  In such cases, the $f$ to
be localized is presumably selected by FPF.  However, in case our
localization approach is used in a setting where single faults are
expected, we propose an alternative method: let $f$ be an arbitrary
test with as few repairing mutants as possible.

>>>>

Parnin and Orso note that most popular methods are
statistical and tend to simply provide an ordered list of statements
to examine.  These statements are not guaranteed to be essentially
related to the fault --- with many techniques, the statements are,
too often, code that executes as a consequence of the fault, code
accidentally executed with the fault, and so forth.  We note that most
evaluations of fault localization have been performed over programs
where it is not clear that debugging is extremely hard, vs. the time
spent applying automated localization and establishing effective
(automated) testing to support automated localization.  Compiler
debugging, on the other hand, especially for subtle optimization-based
problems that produce incorrect code (vs. simple crashes) is generally
known to be difficult.
Researchers reporting subtle compiler bugs often observe the time from
reporting a fault to its correction, even once the fault is assigned,
to be lengthy, and the resulting patches are sometimes thousands of
lines \cite{PLDI13}.  Important compilers, whether JITs where security is paramount
or C compilers used to compile core systems code, also tend to already
be the
subjects of extensive automated testing \cite{jsfunfuzz,csmith}.

@@

In general, we expect {\bf Repair} to be used in the context of
compiler (or other complex system) fuzzing, where there are numerous
failing tests, likely from multiple faults.  In such cases, the $f$ to
be localized is presumably selected by FPF.  However, in case our
localization approach is used in a setting where single faults are
expected, we propose an alternative method: let $f$ be an arbitrary
test with as few repairing mutants as possible, to allow the distance
metric to focus attention on a few key mutants.

### 2017-05-08 othertools.tex
ok to ship

The {\bf Repair} localization was designed for use in compiler (or at least complex system software) fuzzing.  It is not proposed (or at least, not here evaluated) as a general-purpose fault localization method.  However, it is possible to compare {\bf Repair} with other methods, using their full mutation and experimental set, to provide a more apples-to-apples comparison than the evaluation vs. MUSE and MUSEUM over compiler faults.  We obtained the data from two evaluations of mutant-based fault localization methods:  the set of faults used to evaluate MUSEUM \cite{multilingual}, and a set of CoreBENCH \cite{CoreBENCH} faults used in an evaluation of MUSE and Metallaxis-FL by Chekal et. al \cite{Papadakis} (we were unable to obtain the original MUSE dataset, thus far).  These data sets are not ideal for evaluating {\bf Repair}: for all but 10 of the faults (all from the CoreBENCH set) there is only a single failing test case in the data.  {\bf Repair} for single failing tests is essentially MUSEUM without use of passing tests, except to reject any mutation that breaks a passing test.  {\bf Repair} is meant to operate in the case where a program either has numerous failing tests associated with open bugs (e.g., a typical production compiler or complex system software program) or where a program has just been fuzzed for the first time, so has numerous failures representing different faults.  The distance metric lets {\bf Repair} make use of these other faults, by enabling it to focus on repairing mutants most relevant to the failing test.

@@

\subsubsection{CoreBENCH Results} For the full data set in the paper \cite{Papadakis}, {\bf Repair} does not perform as well as MUSE and Metallaxis-FL, as expected.   It is only able to  rank a faulty line of code for 12 of 30 faults.  However, for these faults, it performs very well indeed, perfectly localizing 7 of the 12.  {\bf Repair} is uniquely best for 5 of the 12, and is tied for best for another 6; for the remaining fault, it performs better than Metallaxis-FL but worse than MUSE.  Table \ref{otherbugs} shows the results.  The fourth column shows, for those bugs where {\bf Repair} did not rank any faulty statement, how many statements {\bf Repair} proposed for a user to examine.  Note that in most cases if {\bf Repair} was not helpful it also provided little output to waste a user's time: it only once presented more than 3 statements to examine.   In practice, we only suggest using {\bf Repair} at all in cases where 1) there is at least one repairing mutant (not killed by any passing test) for a failing test and 2) there are multiple failing tests (whether from one or multiple faults).  When the Lines column shows a bold 0, it indicates there were no repairs (7 of the 30 faults).  The 7 faults meeting both requirements are bolded.  For 4 of these, {\bf Repair} produces a perfect localization, and for the other three, it produces no more than 2 non-faulty statements to examine.

\begin{table}
\caption{Fault localization for CoreBENCH faults}
\centering
{\scriptsize
\begin{tabular}{|c|c||c|c||c|c|}
\hline
& \#Failing & & & & \\
Fault & Tests & Repair & Lines & Metallaxis-FL & MUSE\\
\hline
{\bf Coreutils 1} & 2 & 1 & - & 1 & 1 \\
Coreutils 2 & 3 & - &  {\bf 0} & 86 & 186 \\
Coreutils 3 & 1 & 25 & - & 47 & 27 \\
Coreutils 4 & 1 & - &  {\bf 0} & 28 & 431 \\
{\bf Coreutils 5} & 5 & - &  2 & 4 & 7 \\
Coreutils 6 & 1 & - &  1 & 5 & 206 \\
Coreutils 7 & 1 & 1 & - & 5 & 9 \\
Coreutils 8 & 1 & - &  1 & 22 & 160 \\
{\bf Coreutils 9} & 5 & - &  1 & 10 & 157 \\
Coreutils 11 & 1 & - &  1 & 2 & 1 \\
Coreutils 12 & 2 & - & {\bf 0} & 6 & 9 \\
Coreutils 13 & 1 & - & {\bf 0} & 905 & 833 \\
Coreutils 14 & 1 & 14 & - & 19 & 11 \\
{\bf Coreutils 15} & 2 & 1 & - & 1 & 6 \\
Coreutils 16 & 1 & - & {\bf 0} & 569 & 447 \\
{\bf Coreutils 17} & 3 & - &  2 & 37 & 195 \\
Coreutils 18 & 1 & - &  3 & 27 & 3 \\
Coreutils 19 & 1 & 1 & - & 3 & 1 \\
{\bf Coreutils 20} & 7 & 1 & - & 12 & 3 \\
Coreutils 21 & 2 & - & {\bf 0} & 20 & 191 \\
{\bf Coreutils 22} & 2 & 1 & - & 6 & 2 \\
Findutils 27 & 1 & - &  9 & 12 & 6 \\
Findutils 32 & 1 & - &  1 & 73 & 70 \\
Findutils 33 & 1 & - &  3 & 10 & 30 \\
Findutils 35 & 1 & 1 & - & 1 & 1 \\
Findutils 36 & 1 & 9 & - & 9 & 19 \\
Findutils 37 & 1 & 11 & - & 22 & 34 \\
Grep 46 & 1 & - &  2 & 7 & 10 \\
Grep 47 & 1 & 4 & - & 4 & 4 \\
Grep 48 & 1 & - & {\bf 0} & 26 & 497 \\

>>>>

The {\bf Repair} localization was designed for use in compiler (or at least complex system software) fuzzing.  It is not proposed (or at least, not here evaluated) as a general-purpose fault localization method.  However, it is possible to compare {\bf Repair} with other methods, using their full mutation and experimental set, to provide a more apples-to-apples comparison than the evaluation vs. MUSE and MUSEUM over compiler faults.  We obtained the data from two evaluations of mutant-based fault localization methods:  the set of faults used to evaluate MUSEUM \cite{multilingual}, and a set of CoREBench \cite{CoREBench} faults used in an evaluation of MUSE and Metallaxis-FL by Chekal et. al \cite{Papadakis} (we were unable to obtain the original MUSE dataset, thus far).  These data sets are not ideal for evaluating {\bf Repair}: for all but 10 of the faults (all from the CoREBench set) there is only a single failing test case in the data.  {\bf Repair} for single failing tests is essentially MUSEUM without use of passing tests, except to reject any mutation that breaks a passing test.  {\bf Repair} is meant to operate in the case where a program either has numerous failing tests associated with open bugs (e.g., a typical production compiler or complex system software program) or where a program has just been fuzzed for the first time, so has numerous failures representing different faults.  The distance metric lets {\bf Repair} make use of these other faults, by enabling it to focus on repairing mutants most relevant to the failing test.

@@

\subsubsection{CoREBench Results} For the full data set in the paper \cite{Papadakis}, {\bf Repair} does not perform as well as MUSE and Metallaxis-FL, as expected.   It is only able to  rank a faulty line of code for 12 of 30 faults.  However, for these faults, it performs very well indeed, perfectly localizing 7 of the 12 (vs. 3 total perfect localizations for Metallaxis-FL and 4 for MUSE).  {\bf Repair} is uniquely best for 5 of the 12, and is tied for best for another 6; for the remaining fault, it performs better than Metallaxis-FL but worse than MUSE.  Table \ref{otherbugs} shows full results.  The fourth column shows, for those bugs where {\bf Repair} did not rank any faulty statement, how many statements {\bf Repair} proposed for a user to examine.  Note that in most cases if {\bf Repair} was not helpful it also provided little output to waste a user's time: it only once presented more than 3 statements to examine.   In practice, we only suggest using {\bf Repair} at all in cases where 1) there is at least one repairing mutant (not killed by any passing test) for a failing test and 2) there are multiple failing tests (whether from one or multiple faults).  When the Lines column shows a bold 0, it indicates there were no repairs (7 of the 30 faults).  The 7 faults meeting both requirements are bolded.  For 4 of these, {\bf Repair} produces a perfect localization, and for the other three, it produces no more than 2 non-faulty statements to examine.

\begin{table}
\caption{Fault localization for CoREBench faults}
\centering
{\scriptsize
\begin{tabular}{|c|c||c|c||c|c|}
\hline
& \#Failing & & & & \\
Fault & Tests & Repair & Lines & Metallaxis-FL & MUSE\\
\hline
{\bf Coreutils 1} & 2 & 1 & - & 1 & 1 \\
Coreutils 2 & 3 & - &  {\bf 0} & 86 & 186 \\
Coreutils 3 & 1 & 25 & - & 47 & 27 \\
Coreutils 4 & 1 & - &  {\bf 0} & 28 & 431 \\
{\bf Coreutils 5} & 5 & - &  2 & 4 & 7 \\
Coreutils 6 & 1 & - &  1 & 5 & 206 \\
Coreutils 7 & 1 & 1 & - & 5 & 9 \\
Coreutils 8 & 1 & - &  1 & 22 & 160 \\
{\bf Coreutils 9} & 5 & - &  1 & 10 & 157 \\
Coreutils 11 & 1 & - &  1 & 2 & 1 \\
Coreutils 12 & 2 & - & {\bf 0} & 6 & 9 \\
Coreutils 13 & 1 & - & {\bf 0} & 905 & 833 \\
Coreutils 14 & 1 & 14 & - & 19 & 11 \\
{\bf Coreutils 15} & 2 & 1 & - & 1 & 6 \\
Coreutils 16 & 1 & - & {\bf 0} & 569 & 447 \\
{\bf Coreutils 17} & 3 & - &  2 & 37 & 195 \\
Coreutils 18 & 1 & - &  3 & 27 & 3 \\
Coreutils 19 & 1 & 1 & - & 3 & 1 \\
{\bf Coreutils 20} & 7 & 1 & - & 12 & 3 \\
Coreutils 21 & 2 & - & {\bf 0} & 20 & 191 \\
{\bf Coreutils 22} & 2 & 1 & - & 6 & 2 \\
Findutils 27 & 1 & - &  9 & 12 & 6 \\
Findutils 32 & 1 & - &  1 & 73 & 70 \\
Findutils 33 & 1 & - &  3 & 10 & 30 \\
Findutils 35 & 1 & 1 & - & 1 & 1 \\
Findutils 36 & 1 & 9 & - & 9 & 19 \\
Findutils 37 & 1 & 11 & - & 22 & 34 \\
Grep 46 & 1 & - &  2 & 7 & 10 \\
Grep 47 & 1 & 4 & - & 4 & 4 \\
Grep 48 & 1 & - & {\bf 0} & 26 & 497 \\
